### 2020-06-22 manuscript/report_appendix.Rmd
update report

---
suppress-bibliography: true
---

@@

tab.exp.tr <- matrix(round(backtrans(getpars(A2017.fit[[3]][[3]][[4]]$model))[5:20], 2), 4, 4, byrow = T)

apa_table(tab.exp.tr,
          col.names = as.character(1:4),
          col_spanners = list("To state" = c(1,4)),
          row.names = TRUE,
          added_stub_head = "From\nstate",
          caption = "(ref:tab-example-trans)",
          note = "(ref:tab-example-trans-note)")

@@

tab.exp.resp <- matrix(round(backtrans(getpars(A2017.fit[[3]][[3]][[4]]$model))[21:44], 2), 4, 6, byrow = T)

@@

apa_table(tab.exp.resp,
          col.names = c("Shape (vel)", "Scale (vel)", "Shape (acc)", "Scale (acc)", "Mean", "Con"),
          row.names = TRUE,
          format.args = list(na_string = "-"),
          added_stub_head = "State",
          caption = "(ref:tab-example-resp)",
          note = "(ref:tab-example-resp-note)")

>>>>

@@

tab.exp.tr <- cbind(1:4, matrix(round(backtrans(getpars(A2017.fit[[3]][[3]][[4]]$model))[5:20], 2), 4, 4, byrow = T))

apa_table(tab.exp.tr,
          col.names = c("From\nstate", as.character(1:4)),
          col_spanners = list("To state" = c(2,5)),
          caption = "(ref:tab-example-trans)",
          note = "(ref:tab-example-trans-note)")

@@

tab.exp.resp <- cbind(1:4, matrix(round(backtrans(getpars(A2017.fit[[3]][[3]][[4]]$model))[21:44], 2), 4, 6, byrow = T))

@@

apa_table(tab.exp.resp,
          col.names = c("State", "Shape (vel)", "Scale (vel)", "Shape (acc)", "Scale (acc)", "Mean", "Con"),
          format.args = list(na_string = "-"),
          caption = "(ref:tab-example-resp)",
          note = "(ref:tab-example-resp-note)")
